---
title: "Behavioural Drivers to Climate-smart Agriculture: Evidence from Cameroon and Kenya"
#author: 'Martin Paul Jr, Tabe-Ojong, Marvin E., Kedinga & Bisrat Haile Gebrekidan'
date: "Last updated: `r Sys.time()`"
output: 

 bookdown::pdf_document2:
    keep_tex: true
    template: HelperUtilities/my_templet.tex
 odt_document:
header-includes:
   - \usepackage[margin=2.8cm]{geometry}
   - \renewcommand{\contentsname}{Table of Contents}
   - \usepackage{enumitem}
   - \usepackage{pifont}
   - \renewcommand{\labelitemi}{$\rightarrow$}
   - \usepackage{tocloft}
   - \renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
   - \usepackage{hyperref}
   - \hypersetup{linkcolor = blue}
   - \usepackage{hanging}
   - \usepackage[T1]{fontenc}
   - \usepackage{graphicx}
   - \usepackage{booktabs,threeparttablex}
   - \usepackage{pdflscape}
   - \usepackage{fvextra}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
   - \usepackage{lmodern}
   - \usepackage{nimbusmono}
   - \renewcommand{\thetable}{SM\arabic{table}}
   - \setlength{\cfttabnumwidth}{1cm}

toc: false
toccolor: 'blue'
mainfont: 'lm'
toc-title: "-"
---
\newpage
\listoftables
\newpage


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = FALSE,
  warning = FALSE,
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 10),
  # if knitting to html disable the following line
  dev = "cairo_pdf",
  out.width = "100%"
)

options(width = 100)
# load the required libraries
extrafont::loadfonts()

# load the required libraries
pacman::p_load(
  sjlabelled,
  labelled,
  ggthemes,
  haven,
  openxlsx,
  tidyverse
)

#ggthemr(palette = 'light')
#my_font <- font_an
```


```{r}
source("HelperUtilities/Utils.R", local = knitr::knit_global())
my_font <- "Frutiger"
```

```{r}
data_for_plotting_ori <- read_csv("stata_outputs/figures_table/coefficent_tbl.csv")%>%
  janitor::clean_names()

aspiration_df <- haven::as_factor(haven::read_dta("aspirations_investments_2.dta"), only_labelled = TRUE)
```

```{r}
df_plot <- data_for_plotting_ori%>%
  mutate(p.label = case_when(
    !is.na(aster) ~paste0(round(coef,3), aster) ,
    TRUE ~ paste0(round(coef,3), "")
  ) )
```

# Write a generic function

The `plot_coefficents` function allows to generate a coefficient plot with customizable aesthetics and filtering options, providing a visual representation of coefficient estimates, confidence intervals, and significance levels for different variables using the ggplot2 package in R. 

1. The function takes two arguments: `tbl_Num` and `X`, which determine the filtering and aesthetics of the plot, respectively.

2. The function filters the data frame `df_plot` based on the value of `tbl_Num`, keeping only the rows where the `tbl_no` variable matches `tbl_Num`.

3. The ggplot object `plt_tbl_1` is created, specifying the data frame `df_tbl_1` as the data and defining the aesthetics using `aes_string`. The `x` axis is set to the variable passed to the `X` argument, and the `y` axis is set to "coef". The color of the points is determined by the "inters_var" variable.

4. Several ggplot layers are added to the plot:
   - `geom_hline`: Adds a horizontal line at y = 0, representing the baseline/reference line.
   - `geom_point`: Adds points to the plot, representing coefficient estimates. The `position_dodge` function is used to separate the points based on the "inters_var" variable.
   - `geom_errorbar`: Adds error bars to the points, representing confidence intervals for the coefficient estimates.
   - `geom_text`: Adds text labels to the plot,  containing coefficient estimate and significance level . The labels are positioned using `position_dodge` to align them with the points.

5. Axis labels, facetting, and theme customization are applied:
   - `scale_x_discrete`: Sets custom labels for the x-axis categories.
   - `facet_wrap`: Creates separate plots for different levels of the `dep_var` variable.
   - `labs`: Sets the labels for the y-axis, title, subtitle, and x-axis.
   - `ggthemes::theme_base`: Applies a basic theme to the plot.
   - `theme`: Customizes various aspects of the plot, such as the legend position, text size and font, and panel appearance.

6. Finally, it returns the created plot object `plt_tbl_1`.



```{r}
plot_coefficents <- function(tbl_Num=2, X="inters_var"){
  
  df_tbl_1 <- df_plot%>%
  filter(tbl_no==tbl_Num)

  plt_tbl_1 <- 
    ggplot(df_tbl_1, aes_string(x = X, y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
  scale_x_discrete(labels=c("Adoption", "Area under\nadoption (ha)")) +
    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
       strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  
  return(plt_tbl_1)
  
}
```


# Figure 1. CSA practices by country

```{r}


df <- aspiration_df%>%
  select(interview__key, country, fallowing, manure, intercropping, crop_rotation)%>%
  pivot_longer(cols = c(fallowing, manure, intercropping, crop_rotation))%>%
  mutate(name2 = str_to_sentence(name))%>%
  mutate(name2 = case_when(
    name2=="Crop_rotation" ~ "Crop rotation",
    name2=="Manure" ~ "Organic soil\namendments",
    TRUE ~ name2
  ))%>%
  select(-name)%>%
  group_by(country, name2, value)%>%
  summarise(count = n()) %>%
   mutate(ptg = round(prop.table(count) *
        100, 1))%>%
  filter(value==1)

ss <- ggplot(df, aes(x = name2,
    y = ptg)) + geom_bar(aes(fill = country),
    stat = "identity",
    color = "white",
    position = position_dodge(0.8),
    size = 0.3, alpha = 0.9,
    width = 0.7) + 
  geom_text(aes(
    label = paste0(ptg, "%"),group=country), color = "black",  vjust=-0.3, family=my_font,size=5,
    position = position_dodge(.8)) +
    theme_bw(base_family = my_font,
    base_size = 16) +
  labs(y="Percent of households", x="CSA practices")+
    scale_y_continuous(labels = scales::label_percent(scale = 1)) +
    scale_fill_manual(values = c("#1f5e77","#e3542a", "#EEAB73")) +
    #scale_fill_manual(values = c("#305596", "#305596", "#305596"))+
  ylim(c(0,80)) +
    theme(panel.grid.major.y = element_blank(),
          legend.position = "bottom",
          legend.title = element_blank(),
          axis.title = element_text(color = "#51585F"),
        panel.grid.major.x = element_line(size = 0.3),
        panel.grid.minor.y = element_line(size = 0.3), panel.border = element_rect(colour = "grey60"))

ss

ggsave("figures/fig_1.pdf", plot = ss, width = 20, height = 15, units = "cm",device = cairo_pdf)
ggsave("figures/fig_1.png", plot = ss, width = 20, height = 15, units = "cm")

```
# Figure 2. Estimates of aspirations and CSA practices

```{r}
 df_tbl_2 <- df_plot%>%
  filter(tbl_no==2)
 

  
plt_tbl_2 <- 
    ggplot(df_tbl_2, aes_string(x = "dep_var", y = "coef", colour = "dep_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73", "#056B55"))+
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.15, linetype = 3, colour = "grey"),

      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_2
  
  ggsave("figures/fig_2.pdf", plt_tbl_2, width = 32, height = 18, units = "cm",device = cairo_pdf)
  ggsave("figures/fig_2.png", plt_tbl_2, width = 32, height = 18, units = "cm")

```

# Figure 3. Estimates of aspirations failure and CSA practices


```{r}
 df_tbl_3 <- df_plot%>%
  filter(tbl_no==3)%>%
  mutate(inters_var=factor(inters_var, levels = c("Aspiration gap (0-1)","Gap squared (0-1)"),labels  = c("Aspiration\ngap ","Gap\nsquared")))

  
plt_tbl_3 <- 
    ggplot(df_tbl_3, aes_string(x = "inters_var", y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73", "#056B55"))+
    facet_grid(.~dep_var, scales = "free") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#679DBB", alpha.f = 0.5), color = "#679DBB"),
 panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.15, linetype = 3, colour = "grey"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_3
  
ggsave("figures/fig_3.pdf", plt_tbl_3, width = 32, height = 18, units = "cm",device = cairo_pdf)
ggsave("figures/fig_3.png", plt_tbl_3, width = 32, height = 18, units = "cm")

```

# Figure 4: Estimates of aspirations and CSA practices by country

```{r}
 df_tbl_4 <- df_plot%>%
  filter(tbl_no==4)

  
plt_tbl_4 <- 
    ggplot(df_tbl_4, aes_string(x = "dep_var", y = "coef", colour = "dep_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73", "#056B55"))+
    facet_grid(.~country, scales = "free") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#679DBB", alpha.f = 0.5), color = "#679DBB"),
panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.15, linetype = 3, colour = "grey"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_4
  
ggsave("figures/fig_4.pdf", plt_tbl_4, width = 25, height = 15, units = "cm",device = cairo_pdf)
ggsave("figures/fig_4.png", plt_tbl_4, width = 25, height = 15, units = "cm")

```
# Figure 5: Estimates of aspiration failure and CSA practices by country


```{r}
 df_tbl_5 <- df_plot%>%
  filter(tbl_no==5)%>%
  mutate(inters_var=factor(inters_var, levels = c("Aspiration gap (0-1)","Gap squared (0-1)"),labels  = c("Aspiration\ngap ","Gap\nsquared")))

  
plt_tbl_5 <- 
    ggplot(df_tbl_5, aes_string(x = "inters_var", y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73", "#056B55"))+
    facet_grid(country~dep_var, scales = "free") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#679DBB", alpha.f = 0.4), color = "#679DBB"),
panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.15, linetype = 3, colour = "grey"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_5
  
ggsave("figures/fig_5.pdf", plt_tbl_5, width = 32, height = 20, units = "cm",device = cairo_pdf)
ggsave("figures/fig_5.png", plt_tbl_5, width = 32, height = 20, units = "cm")

```
# Figure 6: MVP of the relationship between aspirations and CSA practices
```{r}
 df_tbl_6 <- df_plot%>%
  filter(tbl_no==6)
  

  
plt_tbl_6 <- 
    ggplot(df_tbl_6, aes_string(x = "dep_var", y = "coef", colour = "dep_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73", "#056B55"))+
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.15, linetype = 3, colour = "grey"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_6
  
  ggsave("figures/fig_6.pdf", plt_tbl_6, width = 25, height = 18, units = "cm",device = cairo_pdf)
  ggsave("figures/fig_6.png", plt_tbl_6, width = 25, height = 18, units = "cm")

```
# Figure 7: MVP of the relationship between aspiration and CSA practices (Marginal Effects)

```{r}
 df_tbl_8 <- df_plot%>%
  filter(tbl_no==8)
  

  
plt_tbl_8 <- 
    ggplot(df_tbl_8, aes_string(x = "dep_var", y = "coef", colour = "dep_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73", "#056B55"))+
    labs(
      y = "Marginal Effects(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),

      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_8
  
  ggsave("figures/fig_8.pdf", plt_tbl_8, width = 25, height = 18, units = "cm",device = cairo_pdf)
  ggsave("figures/fig_8.png", plt_tbl_8, width = 25, height = 18, units = "cm")

```
# Figure 8: MVP of the relationship between aspiration failure and CSA practices

```{r}
 df_tbl_7 <- df_plot%>%
  filter(tbl_no==7)%>%
  mutate(inters_var=factor(inters_var, levels = c("Aspiration gap (0-1)","Gap squared (0-1)"),labels  = c("Aspiration\ngap ","Gap\nsquared")))

  
plt_tbl_7 <- 
    ggplot(df_tbl_7, aes_string(x = "inters_var", y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73", "#056B55"))+
    facet_grid(.~dep_var, scales = "free") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#679DBB", alpha.f = 0.5), color = "#679DBB"),
panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.15, linetype = 3, colour = "grey"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_7
  
ggsave("figures/fig_7.pdf", plt_tbl_7, width = 32, height = 18, units = "cm",device = cairo_pdf)
ggsave("figures/fig_7.png", plt_tbl_7, width = 32, height = 18, units = "cm")

```
# Figure 9: MVP of the relationship between aspiration failure and CSA practices (Marginal Effects)

```{r}
 df_tbl_9 <- df_plot%>%
  filter(tbl_no==9)%>%
  mutate(inters_var=factor(inters_var, levels = c("Aspiration gap (0-1)","Gap squared (0-1)"),labels  = c("Aspiration\ngap ","Gap\nsquared")))

  
plt_tbl_9 <- 
    ggplot(df_tbl_9, aes_string(x = "inters_var", y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73", "#056B55"))+
    facet_grid(.~dep_var, scales = "free") +
    labs(
      y = "Marginal Effects(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#679DBB", alpha.f = 0.5), color = "#679DBB"),
panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.15, linetype = 3, colour = "grey"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_9
  
ggsave("figures/fig_9.pdf", plt_tbl_9, width = 32, height = 16, units = "cm",device = cairo_pdf)
ggsave("figures/fig_9.png", plt_tbl_9, width = 32, height = 16, units = "cm")

```

# Figure 10: Unconditional correlations in participation in CSA


```{r}

df <- readr::read_delim(here::here("stata_outputs", "SM_tables", "Table_SM7.txt"), delim = "\t", escape_double = FALSE, trim_ws = TRUE, skip = 1,na = "empty" )

df2 <- df%>%
  select(LABELS,starts_with("atan"))%>%
  filter(LABELS=="Constant")%>%
  pivot_longer(cols = starts_with("atan"))%>%
  select(-LABELS)

# First, install necessary package
library(corrplot)
library(reshape2)

# Create a 4x4 correlation matrix
rho <- matrix(0, nrow=4, ncol=4)
rho[1,2] <- -0.0102
rho[1,3] <- 0.491
rho[1,4] <- 0.324
rho[2,3] <- 0.186
rho[2,4] <- 0.217
rho[3,4] <- 0.173

# Because the matrix is symmetric, we fill in the lower half based on the upper half
rho[lower.tri(rho)] <- t(rho)[lower.tri(rho)]

# Diagonal elements of a correlation matrix are always 1
diag(rho) <- 1

# Convert your values back to correlation scale
corr <- rho

# Create correlation labels with the stars as you provided
corr.labels <- matrix("", nrow=4, ncol=4)
corr.labels[1,2] <- "-0.01"
corr.labels[1,3] <- "0.49***"
corr.labels[1,4] <- "0.32***"
corr.labels[2,3] <- "0.19*"
corr.labels[2,4] <- "0.22**"
corr.labels[3,4] <- "0.17*"

# Because the matrix is symmetric, we fill in the lower half based on the upper half
corr.labels[lower.tri(corr.labels)] <- t(corr.labels)[lower.tri(corr.labels)]

# Diagonal labels - usually they are 1 in a correlation matrix
diag(corr.labels) <- "1"


corr_df <- melt(corr)
names(corr_df) <- c("Var1", "Var2", "value")
corr_df$labels <- c(corr.labels)
corr_df <- corr_df[corr_df$Var1 > corr_df$Var2,]
# Convert Var1 and Var2 to factors for plotting
corr_df$Var1 <- factor(corr_df$Var1, levels = 1:4, labels = c("Crop rotation",	"Intercropping", "Fallowing",	"Organic soil\namendments"))
corr_df$Var2 <- factor(corr_df$Var2, levels = 1:4, labels = c("Crop rotation",	"Intercropping", "Fallowing",	"Organic soil\namendments"))
# Filter the data frame to only include the lower half of the matrix

corr_df
# Plot using ggplot2
# Plot using ggplot2
plt_tbl_10 <- ggplot(data = corr_df, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(high = "#056B55", low = "#8c0049", mid = "white", 
                       midpoint = 0.1, limit = c(-1,1), space = "Lab", 
                       name="Correlation\ncoefficient") +
  geom_text(aes(label=labels), color = "black", size = 5) +
  labs(x="", y="") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggthemes::theme_base() +
    theme(
      #legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.2, linetype = 3, color = "grey"),

      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))


plt_tbl_10

ggsave("figures/fig_10.pdf", plt_tbl_10, width = 20, height = 14, units = "cm",device = cairo_pdf)
ggsave("figures/fig_10.png", plt_tbl_10, width = 20, height = 14, units = "cm")



```

```{r}

df <- readr::read_delim(here::here("stata_outputs", "SM_tables", "Table_SM8.txt"), delim = "\t", escape_double = FALSE, trim_ws = TRUE, skip = 1,na = "empty" )

df2 <- df%>%
  select(LABELS,starts_with("atan"))%>%
  filter(LABELS=="Constant")%>%
  pivot_longer(cols = starts_with("atan"))%>%
  select(-LABELS)


df2$value
# First, install necessary package
library(corrplot)
library(reshape2)

# Create a 4x4 correlation matrix
rho <- matrix(0, nrow=4, ncol=4)
rho[1,2] <- -0.0154
rho[1,3] <- 0.487
rho[1,4] <- 0.330
rho[2,3] <- 0.173
rho[2,4] <- 0.209
rho[3,4] <- 0.170

# Because the matrix is symmetric, we fill in the lower half based on the upper half
rho[lower.tri(rho)] <- t(rho)[lower.tri(rho)]

# Diagonal elements of a correlation matrix are always 1
diag(rho) <- 1

# Convert your values back to correlation scale
corr <- rho

# Create correlation labels with the stars as you provided
corr.labels <- matrix("", nrow=4, ncol=4)
corr.labels[1,2] <- "-0.015"
corr.labels[1,3] <- "0.487***"
corr.labels[1,4] <- "0.330***"
corr.labels[2,3] <- "0.173*"
corr.labels[2,4] <- "0.209**"
corr.labels[3,4] <- "0.170*"

# Because the matrix is symmetric, we fill in the lower half based on the upper half
corr.labels[lower.tri(corr.labels)] <- t(corr.labels)[lower.tri(corr.labels)]

# Diagonal labels - usually they are 1 in a correlation matrix
diag(corr.labels) <- "1"


corr_df <- melt(corr)
names(corr_df) <- c("Var1", "Var2", "value")
corr_df$labels <- c(corr.labels)
corr_df <- corr_df[corr_df$Var1 > corr_df$Var2,]
# Convert Var1 and Var2 to factors for plotting
corr_df$Var1 <- factor(corr_df$Var1, levels = 1:4, labels = c("Crop rotation",	"Intercropping", "Fallowing",	"Organic soil\namendments"))
corr_df$Var2 <- factor(corr_df$Var2, levels = 1:4, labels = c("Crop rotation",	"Intercropping", "Fallowing",	"Organic soil\namendments"))
# Filter the data frame to only include the lower half of the matrix

corr_df
# Plot using ggplot2
# Plot using ggplot2
plt_tbl_11 <- ggplot(data = corr_df, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(high = "#056B55", low = "#8c0049", mid = "white", 
                       midpoint = 0.1, limit = c(-1,1), space = "Lab", 
                       name="Correlation\ncoefficient") +
  geom_text(aes(label=labels), color = "black", size = 5) +
  labs(x="", y="") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  ggthemes::theme_base() +
    theme(
      #legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.2, linetype = 3, color = "grey"),

      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))


plt_tbl_11

ggsave("figures/fig_11.pdf", plt_tbl_10, width = 20, height = 14, units = "cm",device = cairo_pdf)
ggsave("figures/fig_11.png", plt_tbl_10, width = 20, height = 14, units = "cm")



```

```{r}

df <- aspiration_df%>%
  select(crop_rotation, intercropping, fallowing, manure)
# If not installed, install necessary packages
if (!require(gplots)) install.packages('gplots')

library(gplots)

# Assuming your dataframe is named df
# Replace 'df' with your actual dataframe's name

# Create an empty matrix for storing the results
percentages_mat <- matrix(0, nrow = ncol(df), ncol = ncol(df))
rownames(percentages_mat) <- colnames(df)
colnames(percentages_mat) <- colnames(df)

# Calculate the percentage of households that adopted both practices
for(i in seq_along(df)) {
  for(j in seq_along(df)) {
    percentages_mat[i, j] <- mean(df[[i]] * df[[j]]) * 100
  }
}

# Convert the matrix to a dataframe
percentages_df <- as.data.frame(percentages_mat)

# Convert rownames to a column
percentages_df$Practice1 <- rownames(percentages_mat)

# Melt the dataframe
melted_df <- reshape2::melt(percentages_df, id.vars = "Practice1")

# Rename the variables for clarity
colnames(melted_df) <- c("Practice1", "Practice2", "Percentage")

melted_df <- melted_df%>%
   mutate(Practice1 = str_to_sentence(Practice1))%>%
   mutate(Practice1 = case_when(
   Practice1=="Manure" ~ "Organic soil\namendments",

    Practice1=="Crop_rotation" ~ "Crop rotation",
    TRUE ~ Practice1
  ))%>%
   mutate(Practice2 = str_to_sentence(Practice2))%>%
   mutate(Practice2 = case_when(
   Practice2=="Manure" ~ "Organic soil\namendments",

    Practice2=="Crop_rotation" ~ "Crop rotation",
    TRUE ~ Practice2
  ))

# Create a heatmap using ggplot2
mm <- ggplot(data = melted_df, aes(x=Practice1, y=Practice2, fill=Percentage)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "#019d9c") +
  theme_minimal(base_family = my_font, base_size = 18) +
  theme(axis.text.x = element_text( hjust = 0.5), text = element_text(family = my_font)) +
  labs(x='', y='', title='', fill='Percentage') +
  geom_text(aes(label=round(Percentage, 1)), size=5, family=my_font)


ggsave("figures/fig_12.pdf", mm, width = 28, height = 14, units = "cm",device = cairo_pdf)
ggsave("figures/fig_12.png", mm, width = 25, height = 14, units = "cm")

```



```{r}
library(openxlsx)
# Split the data frame based on Category column

df_export <- data_for_plotting_ori%>%
  rename(`Interest variables` = inters_var, `Outcome variables` = dep_var, Coefficent = coef, `Robust standard error`=se, `P-Value` = pval, Significance = aster, `Confidence Interval (lower)`= ci_low,`Confidence Interval (upper)`=ci_high, `R-Square`= r_sqr, `Model type` = model_type, Country = country)

df_list <- split(df_export, df_export$tbl_no)

# Create a new workbook
wb <- createWorkbook()

# Save each subset as an Excel sheet
for (i in seq_along(df_list)) {
  sheet_name <- paste("Figure_", names(df_list)[i], sep = "")
  addWorksheet(wb, sheetName = sheet_name)
  writeData(wb, sheet = sheet_name, x = df_list[[i]])
}

# Save the workbook as an Excel file
saveWorkbook(wb, "Source_Data_2_0.xlsx", overwrite = TRUE)
```
